Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-02-04 PaperVictor.tex
Small corrections.

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional structures with less
than 100 pairs of layers. We obtained a structure that has the an
omnidirectional spectral width larger than those previously
reported.
\end{abstract}

\section{Introduction}

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. 
\notaL{Any reason
	for these choices? They seem arbitrary.} \notaL{Creo que alguna 
	explicación  sencilla merece el lector.} 
\notaV{Agregue:  }
Approximately $90\%$ of the solar radiation that reaches the 
earth's surface is contained in the spectral region of 350 to 1400 
nm ($\mathcal R_1$), while in ($\mathcal R_2$) it can be up 
to $98\%$ of terrestrial solar radiation \cite{Bird1983}. A direct 
application of the optimized structures in these regions is solar 
reflectors.
The
optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.

\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC).}
\end{table}
\notaL{¿Sería
	correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
	nuestra definición?}
\notaV{Agregue:   }
Various photonic structures have been obtained with $R>90\%$ 
\cite{Xu2018,Ahmed2014,Reiner2000}, so we also report 
omnidirectional spectra band (ODB) with $R>90\%$ for all angles.
The function $f_{3}$ yields after optimization the highest 
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest 
structure. Furthermore, this
structure has an ODB of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). 
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.}
\end{figure}

@@

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos KD = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector and $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
photonic band gap within which we
expect a high reflectance, even for a finite system made of only a few periods. This suggests
the following design strategy. We stack sub-mirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
sub-mirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. This is particularly important
for sub-mirrors tuned to shorter wavelengths, for which there is some
absorption. We followed thus two design
strategies: In the first, we considered sub-mirrors each with the same
number $p$ of periods. In the second, a different number of periods was
assigned to each sub-mirror according to the center of its PBG: we chose
a single period for those sub-mirrors $j$ tuned to
$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
three periods for $650<\lambda_ {j}<800$ nm, and for
$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
4 and 10. In both designs, the degree of overlap of consecutive PBGs was
taken as the parameter to be optimized in order to maximize
the reflectance $\braket{R}$ averaged within the spectral and
angular range $400\text{ nm}\le
\lambda\le 3000\text{ nm}$ and for $0^\circ\le\theta\le90^\circ$.
\notaV{Agregue:   }
We define the percentage of overlap as the portion of the PBG of the $j$-th mirror that has been covered by the PBG of the $(j + 1)$-th mirror.
 \notaL{¿Valdría la pena
  definir este overlap?}
\notaV{No entend\'{i} esta observaci\'{o}n.}
\notaL{En el texto no se aclara como defines el porcentaje de traslape
  de dos bandas. Valdría la pena definirlo para que el lector entiende
  qué significan los números en la tabla. Para mí no es obvio. Tienes
  el ancho de una banda, el ancho de la otra y el ancho de la región
  en que se traslapan. ¿Cómo combinas dichos números para producir un
  porcentaje de overlap?}

@@

We have designed, fabricated and characterized highly reflective quasi
omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range, optimized through two techniques: chirping and
stacking of Bragg-type sub-structures. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to maximize the reflectance averaged over different spectral ranges and for
all angles. We manufactured some of the optimized structures with
porous silicon
dielectric multilayers and compared their measured  optical properties
to the results of calculations. We fabricated two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm centered
at 1160 nm and 1925 nm, respectively. We fabricated a
stacked structures  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
with a bandwidth of 1800 nm centered at 1850 nm. 
\notaV{Agregue:    } Thus, the results we have shown are very good for all three structures.
%Therefore, the second technique is found to be better as it results in thiner structures with a noticeable improvement in the average reflectance.
\notaL{No me es clara la conclusión, pues cada muestra fue diseñada para distintas
  regiones. ¿Es justo compararlas? Quizás sólo debamos decir que los resultados fueron muy
  buenos para las tres muestras. \notaV{De Acuerdo} Si alguien quisiera diseñar un espejo específico, ¿sabrías qué
estrategia recomendarle para su diseño?}
\notaV{Si el lector no tiene experiencia acerca de los materiales,
	se aconsejar\'{i}a usar estructuras chirped. Por otra parte, al observar el mapeo de los valores de las trazas de sub
	espejos, se podr\'{i}a diseñar la estructura adecuada a las
	necesidades.} \notaL{Falta meterlo entonces a las conclusiones.}
\notaV{Agregue:   }
Furthermore, if someone without experience wants to obtain an 
optimized photonic structure, we recommend using the chirped type 
structures. There are cases in which it is suggested to use 
sub-mirror stacking, for example, when the absorption of the 
materials is negligible.
Additionally, the analysis techniques developed here can
be used to optimize the reflectance for other refractive index contrasts
in PS multilayers or in different systems with other types of
materials. Such proposed structures could be used as mirrors for solar
concentrators, flat focusing reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with a
wide angular independent response.

>>>>

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional structures with less
than 100 pairs of layers. We obtained a structure that has the an
omnidirectional spectral width larger than those previously
reported.
\end{abstract}
\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
  en los agrads.}
\section{Introduction}

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
\notaL{Any reason
	for these choices? They seem arbitrary.} \notaL{Creo que alguna
	explicación  sencilla merece el lector.}
\notaV{Agregue:  }
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
application of the optimized structures in these regions is solar
reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
  fijo y en el otro caso no? Sería bueno que el lector entienda todas
  las decisiones que sean fáciles de explicar}
The
optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.

\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC).}
\end{table}
\notaL{¿Sería
	correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
	nuestra definición?}
\notaV{Agregue:   }
Various works use $R>90\%$ as a criterium for defining
omnidirectional band, and

The function $f_{3}$ yields after optimization the highest
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
structure. Furthermore, this
structure has an omnidirectional band (ODB) of width (ODW) 250 nm
centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
photonic structures have been reported with
omnidirectional bands (ODB's) \cite{Xu2018,Ahmed2014,Reiner2000} defined
through the criterium $R>90\%$ which we adopt here.
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.}
\end{figure}

@@

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos KD = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector and $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
photonic band gap within which we
expect a high reflectance, even for a finite system made of only a few periods. This suggests
the following design strategy. We stack sub-mirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
sub-mirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. This is particularly important
for sub-mirrors tuned to shorter wavelengths, for which there is some
absorption. We followed thus two design
strategies: In the first, we considered sub-mirrors each with the same
number $p$ of periods. In the second, a different number of periods was
assigned to each sub-mirror according to the center of its PBG: we chose
a single period for those sub-mirrors $j$ tuned to
$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
three periods for $650<\lambda_ {j}<800$ nm, and for
$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
4 and 10. In both designs, the degree of overlap of consecutive PBGs was
taken as the parameter to be optimized in order to maximize
the reflectance $\braket{R}$ averaged within the spectral and
angular range $400\text{ nm}\le
\lambda\le 3000\text{ nm}$ and for $0^\circ\le\theta\le90^\circ$.
\notaV{Agregue:   }
We define the percentage of overlap in terms of the portion of the PBG of the
$j$-th mirror that lies within the PBG of the $(j + 1)$-th
mirror.

@@

We have designed, fabricated and characterized highly reflective quasi
omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range, optimized through two techniques: chirping and
stacking of Bragg-type sub-structures. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to maximize the reflectance averaged over different spectral ranges and for
all angles. We manufactured some of the optimized structures with
porous silicon
dielectric multilayers and compared their measured  optical properties
to the results of calculations. We fabricated two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm centered
at 1160 nm and 1925 nm, respectively. We fabricated a
stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
with a bandwidth of 1800 nm centered at 1850 nm.
\notaV{Agregue:    } Thus, our techniques allowed us to obtain very
good relatively thin quasi omnidirectional mirrors with wide bands
over different wavelength ranges.
\notaL{Me sospecho que es un poco improvisada esta respuesta, pues el
  resultado depende de la región espectral, contrastes, etc. Entiendo
  que estás contestando mi pregunta previa, pero desmerece las
  conclusiones. El lector sin experiencia se quedará en las mismas,
  además de ofendido de que te refieras en el texto a ellos directamente:
Furthermore, if someone without experience wants to obtain an
optimized photonic structure, we recommend using the chirped type
structures. There are cases in which it is suggested to use
sub-mirror stacking, for example, when the absorption of the
materials is negligible.}
Our analysis techniques can
be used for the optimization of the reflectance multilayered PS systems with
different refractive index contrasts or for systems with other types of
materials. Such proposed structures could be used as mirrors for solar
concentrators, flat focusing reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with a
wide angular independent response.
